### 2012-12-19 doc/description.tex
reformated eorm add property

$
\Phi_{addClass}(c, d) = \inference{ \forall t \in tables(d) : name(t) \neq name(\rho(c)) \\
	\forall a \in associations(c), \exists u \in  tables(d) : reference(a) = name(u) 
}{
\begin{gathered}
  \rho(c) \wedge \rho(singleProperties(c)) \wedge \rho(collectionProperties(c)) \\ \wedge \rho(associations(c))
\end{gathered}
}
$
\subsubsection{Add Property}
$
\Phi_{addProperty}(p, d) = \begin{cases}
\inference{ \exists t \in tables(d) : name(t) = name(owningClass(p)) \wedge (! mandatory(p) \vee ! instantiated(owningClass(p))}{ \rho(p,d)} 
\\ \\ 
\inference{ \exists t \in tables(d) : name(t) = name(owningClass(p)) \wedge mandatory(p) \wedge instantiated(owningClass(p)) \wedge cardinality(p) \leq 1}{ \rho(p,d) \wedge \forall r \in data(d), reference(r) = t : pair(r) \cup pair(name(p), defaultValue(p))} 
\\ \\
\inference{ \exists t \in tables(d) : name(t) = name(owningClass(p)) \wedge mandatory(p) \wedge instantiated(owningClass(p)) \wedge cardinality(p) \leq 1}{\begin{gathered}
 \rho(p,d) \wedge \forall r \in row(owningClass(p)) : data(d)\\ \cup row(name(p), pair("value", defaultValue(p)), \\ pair(name(p), value(primaryKey(r))) 
\end{gathered}
}

>>>>

$
\Phi_{addClass}(c, d) = \inference{ \forall t \in tables(d) : name(t) \neq name(\rho(c)) \\
	\forall a \in associations(c), \exists u \in  tables(d) : reference(a) = name(u) 
}{
\begin{gathered}
  \rho(c) \wedge \rho(singleProperties(c)) \wedge \rho(collectionProperties(c)) \\ \wedge \rho(associations(c))
\end{gathered}
}
$
\subsubsection{Add Property}
$
\Phi_{addProperty}(p, d) = \begin{cases}
\inference{ \exists t \in tables(d) : name(t) = name(owningClass(p)) \\ \wedge (! mandatory(p) \vee ! instantiated(owningClass(p))}{ \rho(p,d)} 
\\ \\ 
\inference{ \exists t \in tables(d) : name(t) = name(owningClass(p)) \\ \wedge mandatory(p) \wedge instantiated(owningClass(p)) \\ \wedge cardinality(p) \leq 1}{\begin{gathered}
 \rho(p,d) \wedge \forall r \in data(d), reference(r) = t : pair(r) \\ \cup pair(name(p), defaultValue(p))
\end{gathered}
} 
\\ \\
\inference{ \exists t \in tables(d) : name(t) = name(owningClass(p)) \\ \wedge mandatory(p) \wedge instantiated(owningClass(p)) \\ \wedge cardinality(p) \leq 1}{\begin{gathered}
 \rho(p,d) \wedge \forall r \in row(owningClass(p)) : data(d)\\ \cup row(name(p), pair("value", defaultValue(p)), \\ pair(name(p), value(primaryKey(r))) 
\end{gathered}
}
